Handovers

### 2024-02-22 minos/validation/handovers.Rmd
gettting all 4 new mods and intervention working together for test run

out.path <- here::here('output', 'energy_default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

>>>>

#out.path <- here::here('output', 'default_config/')
out.path <- here::here('output', 'energy_default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```
